Non-English Conditional Entropy and Mutual Information

### 2018-11-18 ldp/LDP_entropy.Rmd
ldp ses analysis code

utterances <- get_table(connection, "utterances") %>% collect() #to get the "utterances" table as a dataframe named utterances
DBI::dbListTables(connection) #to list the tables in the collection
```

```{r ldp_analysis}
get_unigram_entropies <- function(role, person, sen_length, utterances) {

  if(role == "child") {
    sub_utterances <- utterances %>%
      filter(subject == person) %>% 
      filter(c_utts_orig != "") %>%
      mutate(length = str_count(c_utts_orig, " |\\+|_") + 1)

      colnames(sub_utterances)[colnames(sub_utterances)=="c_utts_orig"] <- "gloss"
  } else {
     sub_utterances <- utterances %>%
      filter(subject == person) %>% 
      filter(p_utts_orig != "") %>%
      mutate(length = str_count(p_utts_orig, " |\\+|_") + 1)

@@

entropies <- map(2:10, ~get_unigram_entropies("child", , .x, utterances)) %>%
  bind_rows()

>>>>

utterances <- get_table(connection, "utterances") %>% collect() #to get the "utterances" table as a dataframe named utterances
home_visits <- get_table(connection, "home_visits")  %>% collect() #information about SES, work, education and other demographic stuff
DBI::dbListTables(connection) #to list the tables in the collection
```

```{r filter_utterances}
get_ses_utterances <- function(status, utterances, home_visits) {
  income <- home_visits %>% filter(income_category %in% status)

  ids <- unique(income$id) %>% unlist()

  utterances %>% filter(subject %in% ids)
}

ses_utts <- get_ses_utterances(c(6), utterances, home_visits)
```

```{r ldp_analysis}
get_unigram_entropies <- function(role, sen_length, utterances) {

  if(role == "child") {
    sub_utterances <- utterances %>%
      filter(c_utts_orig != "") %>%
      mutate(length = str_count(c_utts_orig, " |\\+|_") + 1)

      colnames(sub_utterances)[colnames(sub_utterances)=="c_utts_orig"] <- "gloss"
  } else {
     sub_utterances <- utterances %>%
      filter(p_utts_orig != "") %>%
      mutate(length = str_count(p_utts_orig, " |\\+|_") + 1)

@@

entropies <- map(2:10, ~get_unigram_entropies("child", .x, ses_utts)) %>%
  bind_rows()
